### 2014-06-06 paper/body.tex
Added a fig
working on figure caption

\begin{figure}[htpb]
\begin{center}
\includegraphics[width=1\linewidth]{drawings/transfer.pdf}
\end{center}
\caption{\edit{Caption here...}}
\label{i}
\end{figure}

>>>>

\begin{figure}[htpb]
\begin{center}
\includegraphics[width=1\linewidth]{drawings/transfer.pdf}
\end{center}
\caption{Overview of the experimental treatments and controls. \emph{Top two rows:} The baseline control involves training a Convolutional Network in the normal way \todo{cite}. Training occurs on only half the dataset (labels A) for consistency with the experimental treatments. The baseline control is repeated for each half of the dataset (labels A and labels B). \emph{Third row:} }
\label{i}
\end{figure}
